Out-of-Sample Comparisons of Overfit Models

### 2014-01-09 paper.tex
Add definition of gamma and eta to Lemma A4
This commit add some definitions to the proof of lemma A4:
- gamma
- delta
- eta
and changes the gamma notation to gamma_T for the proof.
Those terms are used in the proof but had not been defined.

This commit closes #31.

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  then
  \begin{equation}
    \label{eq:12}
    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

Note that $\{Z_{1t}^2 P\gamma/b_T\}$ and $\{Z_{2t}^2 P\gamma/b_T\}$
are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
are bounded in absolute value by $C\sqrt{b_T/P\gamma}$; uniform
integrability ensures that the difference between the unbounded random
variables and these truncated versions is negligible for large enough
values of $C$.

@@

For non-negative $m$, we have
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing half of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
\begin{equation*}
 \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
\end{equation*}
Also define
\begin{equation*}
  Z_{1t}^* = (P\gamma)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma), \\
\end{equation*}
and
\begin{equation*}
Z_{2t}^* = (P\gamma)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma}.
\end{equation*}

Now, we have the inequalities
\begin{align*}
  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
  \\ &\leq
  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
  Z_{1t}Z_{2t} \rVert_2 \\
  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
%  \rVert_2)\return \\
  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
  \rVert_2 \\
  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
  Z_{2t} \rVert_{\infty}
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
  &\leq \frac{2 C b_T^{1/2}}{(P\gamma)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
\end{align*}

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma\Big) =
 o(b_T/\gamma) \to 0,
\]
as required.
\end{proof}

>>>>

\begin{lem}\label{lem:a2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-3} hold.  Let $b_T$ be a
  sequence of integers such that $b_T \to \infty$ and $b_T = o(P)$ and define
  \begin{equation*}
    Z_i = \ZDef.
  \end{equation*}
  Then
  \begin{equation}
    \label{eq:10}
    \sum_{i=1}^{\lfloor P/b_T \rfloor} (\E_R Z_i^2 - \E_{R+(i-1) b_T}
    Z_i^2) \to^p 0.
  \end{equation}
  If Assumptions~\ref{asmp-4} and \ref{asmp-5} also hold and we define
  \begin{gather*}
    Z_{1t} = \varianceTermIIIa, \intertext{and} Z_{2t} =
    \varianceTermIVb,
  \end{gather*}
  with $\delta > 0$, $\eta_\delta$ defined in the proof of
  Lemma~\ref{res-variance-estimator}, and $\gamma_T = b_T/\delta$, then
  \begin{equation}
    \label{eq:12}
    \vtSum (Z_{1t} Z_{2t} - \E_R Z_{1t} Z_{2t}) \to^p 0.
  \end{equation}
\end{lem}
\begin{proof}
\newcommand{\UFiltration}[1]{\ensuremath{\mathcal{F}_{(#1)b_{T}+R-P}}}%
The first result,~\eqref{eq:10}, follows a similar argument to Lemma~5
of \citet{Jon:97} and~\eqref{eq:12} to Lemma~A.4 of \citet{JoD:00}.
Since these arguments are similar and our modification is the same for
both, we'll just present the more complicated version,~\eqref{eq:12}.

Note that $\{Z_{1t}^2 P\gamma_T/b_T\}$ and $\{Z_{2t}^2 P\gamma_T/b_T\}$
are uniformly integrable.  As in~\citet[Lemma A.4]{JoD:00}, we can
assume that there is a constant $C$ such that $Z_{1t}$ and $Z_{2t}$
are bounded in absolute value by $C\sqrt{b_T/P\gamma_T}$; uniform
integrability ensures that the difference between the unbounded random
variables and these truncated versions is negligible for large enough
values of $C$.

@@

For non-negative $m$, we have
\begin{equation*}
U_i - \E_R U_i \in \UFiltration{2i+2m-1},
\end{equation*}
establishing half of the mixingale result trivially.  Now fix $i$ and $m >
0$ and use Lemma \ref{lem-basic-coupling} to define $D_{ts}^*$
for each $t =(2i-2)b_T-P+R+1,\dots,(2i-1)b_T-P+R$ and $s =
\max(t-b_T,R+1),\dots,\min(t+b_T,T-\h)$ such that
\begin{equation*}
 \E_R D_{ts}^* = \E_{(2i-2m-1)b_T+R-P} D_{ts}^* \quad a.s.
\end{equation*}
and
\begin{equation*}
  \lVert D_{ts}^* - D_s \rVert_2 \leq \couplingBound{s - (2i-2m-1)b_T+P}.
\end{equation*}
Also define
\begin{equation*}
  Z_{1t}^* = (P\gamma_T)^{-1/2} \sum_{l=\vttLower}^{\vttUpper}
  (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ W(l/\gamma_T), \\
\end{equation*}
and
\begin{equation*}
Z_{2t}^* = (P\gamma_T)^{-1/2} \sum_{j=\vttLower}^{\vttUpper}
    (D_{t,t+l}^* - \E_R D_{t,t+l}^*)\ \kernelB{j/\gamma_T}.
\end{equation*}

Now, we have the inequalities
\begin{align*}
  \lVert \E( U_i - \E_R U_i & \mid \UFiltration{2i-2m-1}) \rVert_2
  \\ &\leq
  \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) - \E_R
  Z_{1t}Z_{2t} \rVert_2 \\
  &= \vtSuma \lVert \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
  &\quad - \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1}) \\
  &\quad + \E(Z_{1t}^* Z_{2t}^* \mid \UFiltration{2i-2m-1})
  - \E_R Z_{1t}Z_{2t} \rVert_2 \\
%  \leq \vtSuma (\wall \lVert \wall \E(Z_{1t}Z_{2t} \mid \UFiltration{2i-2m-1}) \\
%  - \E(Z_{1t}^*Z_{2t}^* \mid \UFiltration{2i-2m-1}) \rVert_2\return
%  \\ + \lVert \E_R Z_{1t}Z_{2t} - \E_R Z_{1t}^*Z_{2t}^*
%  \rVert_2)\return \\
  &\leq 2 \vtSuma \lVert Z_{1t} Z_{2t} - Z_{1t}^* Z_{2t}^*
  \rVert_2 \\
  &\leq 2 \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2 \lVert
  Z_{2t} \rVert_{\infty}
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2 \lVert Z_{1t}^* \rVert_{\infty}) \\
  &\leq \frac{2 C b_T^{1/2}}{(P\gamma_T)^{1/2}} \vtSuma (\lVert Z_{1t} - Z_{1t}^* \rVert_2
  + \lVert Z_{2t} - Z_{2t}^* \rVert_2).
\end{align*}

And we can finish the proof with the following inequalities:
\begin{align*}
  \frac{2 C b_T^{1/2}}{(P \gamma_T)^{1/2}} &\vtSuma \lVert Z_{1t} - Z_{1t}^* \rVert_2 \\& \leq
  \frac{4C b_T^{1/2}}{P\gamma_T} \vtSuma \sum_{l=\vttLower}^{\vttUpper} \lVert
  D_{t+l} - D_{t,t+l}^* \rVert_2 W(l/\gamma_T) \\&
  \leq O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) \vtSuma
  \sum_{l=\vttLower}^{\vttUpper} \couplingBeta{t+l-(2i-2m-1)b_T+P}\\&
  = O\Bigg(\frac{b_T^{1/2}}{P\gamma_T}\Bigg) O(b_T^{3/2-u}\, m^{-1/2-u})
\end{align*}
for some positive $u$.  The same argument holds for $Z_{2t}$.
As a result,
\[
E\Big(\vtSumr (U_i - \E_R U_i)\Big)^2 = o\Big(\vtSumr b_T^2/P\gamma_T\Big) =
 o(b_T/\gamma_T) \to 0,
\]
as required.
\end{proof}
